Enhancement of SDR in Thessaloniki

### 2024-06-07 GHI_enh_04_investigate.tex
Commit 2024-06-06 14:14
Commit 2024-06-07 00:17
Commit 2024-06-07 11:14
Commit 2024-06-07 12:24

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-06}

@@

\caption{ - empty caption - }\label{fig:rel-energy-5}
\end{figure}

@@

\begin{verbatim}
2024-06-06 09:19:49.0 athan@tyler GHI_enh_04_investigate.R 2.764330 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-07}

@@

\caption{ - empty caption - }\label{fig:rel-energy-5}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-6}

\caption{ - empty caption - }\label{fig:rel-energy-6}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-7}

\caption{ - empty caption - }\label{fig:rel-energy-7}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-8}

\caption{ - empty caption - }\label{fig:rel-energy-8}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/rel-energy-9}

\caption{ - empty caption - }\label{fig:rel-energy-9}
\end{figure}

@@

\begin{verbatim}
2024-06-07 08:51:14.3 athan@tyler GHI_enh_04_investigate.R 1.824008 mins
\end{verbatim}
